A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-05-09 graph_syntax.tex
fixing A vs D

% ((JG: A single variable node can have many incomming driven edges. These edges are 
%    free and can be added or removed from the graph.))
%
%  [[Insert legend for node and edge types]] ((DP: I'm not sure what the legend is supposed to be))

@@

  The variable $x_1$ is usually refered to as a local variable, which is 
  contradicted by the given graph \cite{Sellar1996}. This discrepancy 
  arises from the explicit treatment of objectives and constraints as separate 
  expression blocks. This variable is could be considered a local 
  variable because it directly affects only analysis block $A_1$. However, by expanding
  $F$ into an expression block with its own inputs, $F$ maintains its own local 
  copy of the $x_1$ variable. This formulation necessitates the creation of the global 
  node $x_1^*$ in the graph with two outgoing edges to link the two $x_1$ inputs nodes 
  in the respective blocks.

@@

  In a multi-fidelity problem, a given variable node may have multiple incoming 
  edges without implying a collision as defined by by Eq.~\ref{e:collision}. 
  Fig.~\ref{f:collision_example} shows a modified version of the Sellar problem 
  with a new analysis, $D_0$, representing a low fidelity version of $A_1$. 
  In this modified graph, the annotations indicate the upper indegree limit. For 
  $A_2$, $\txt{deg}^-_u(A_2.y_1) = 2$ which avoids a collsion. A  
  $\txt{deg}^-_u(v) > 1$ for any variable in a graph represents a decision to 
  allow multiple fidelities to interact at that part of the graph in order to allieviate
  a conflict. In section \ref{ss:obtaining FPG} we present an algorithm for finding 
  conflicts within a given MCG so that a designer can make the necessary decisisons about each 
  one in turn. 
  \begin{figure}
    \begin{center}
      %\includegraphics[height=.25\textheight]{}
    [INSERT GRAPH HERE]
    \caption{Graph of the modified Sellar, multi-fidelity problem with $\txt{deg}^-_u(v)$ annotations on variable nodes\label{f:collision_example}}
  \end{center}
  \end{figure}

>>>>

@@

  The variable $x_1$ is usually refered to as a local variable, which is 
  contradicted by the given graph \cite{Sellar1996}. This discrepancy 
  arises from the explicit treatment of objectives and constraints as separate 
  expression blocks. This variable is could be considered a local 
  variable because it directly affects only analysis block $D_1$. However, by expanding
  $F$ into an expression block with its own inputs, $F$ maintains its own local 
  copy of the $x_1$ variable. This formulation necessitates the creation of the global 
  node $x_1^*$ in the graph with two outgoing edges to link the two $x_1$ inputs nodes 
  in the respective blocks.

@@

  In a multi-fidelity problem, a given variable node may have multiple incoming 
  edges without implying a collision as defined by by Eq.~\ref{e:collision}. 
  Fig.~\ref{f:collision_example} shows a modified version of the Sellar problem 
  with a new analysis, $D_0$, representing a low fidelity version of $D_1$. 
  In this modified graph, the annotations indicate the upper indegree limit. For 
  $D_2$, $\txt{deg}^-_u(D_2.y_1) = 2$ which avoids a collsion. A  
  $\txt{deg}^-_u(v) > 1$ for any variable in a graph represents a decision to 
  allow multiple fidelities to interact at that part of the graph in order to allieviate
  a conflict. In section \ref{ss:obtaining FPG} we present an algorithm for finding 
  conflicts within a given MCG so that a designer can make the necessary decisisons about each 
  one in turn. 
  \begin{figure}
    \begin{center}
      %\includegraphics[height=.25\textheight]{}
    [INSERT GRAPH HERE]
    \caption{Graph of the modified Sellar, multi-fidelity problem with $\txt{deg}^-_u(v)$ annotations on variable nodes\label{f:collision_example}}
  \end{center}
  \end{figure}
